# File with summary of data and models
#Not working: forget about for now...
```{r, echo=FALSE, warning=FALSE, include=FALSE}
#Starting from open
setwd("~/LongTermEvolution_Data-Code/Predation_ActivityAggregation/scripts")
#Evolution Pop's: Activity
list=(ls())

source("PredationActivityAnalysisJune2015.R")

#Nieve Flies: Activity

source("ActivityDrosophila_SpiderCues_Nieve.R")


#Evolved Pop's: Mating Behaviours
#source("~/Bioinformatics/Long_Term_Data/Data_LongTermPopulationExperiments_Git/PredationCourtship/scripts/AP_data_R_script.R")
```




###Evolved Activity (light:dark)

```{r, echo=FALSE, warning=FALSE}
with(dat.hourly[dat.hourly$Trt=="C",], 
    plot(Hourly_activity ~ jitter(hour.shifted, factor=1.3), pch=20, cex=0.2,
         xlab ="hours after initiation", ylab = "hourly activity",
         main = "temporal patterns of activity ",
         ylim=c(0,800)))
         
with(dat.hourly[dat.hourly$Trt=="C",], lines(smooth.spline(y=Hourly_activity, x = hour.shifted),lwd=2))

with(dat.hourly[dat.hourly$Trt=="P",], points(Hourly_activity ~ jitter(hour.shifted, factor=1.3), pch=20, cex=0.2, col="red"))
with(dat.hourly[dat.hourly$Trt=="P",], lines(smooth.spline(y=Hourly_activity, x = hour.shifted), col="red", lwd=2))

with(dat.hourly[dat.hourly$Trt=="S",], points(Hourly_activity ~ jitter(hour.shifted, factor=1.3), pch=20, cex=0.2, col="blue"))
with(dat.hourly[dat.hourly$Trt=="S",], lines(smooth.spline(y=Hourly_activity, x = hour.shifted), col="blue", lwd=2))

legend(x=21, y=820, legend=c("LTC", "LTP", "LTS"), pch=20, col=c(1, "red", "blue"))
rect(xleft=2, xright=14, ybottom = 0, ytop = 830, col="#ffff0032", border=NA)

```



###Naive Mean Daily Activity: By monitor and combined

```{r, echo=FALSE, warning=FALSE}

g2 <- plo3+geom_boxplot()
g2
```

###Very Quick linear model for daily activity

```{r, warning=FALSE}
day_act.lmer <- lmer(mean_activity ~ Treatment + monitor + (1|day), data=day_act)
car::Anova(day_act.lmer)
summary(day_act.lmer)
confint(day_act.lmer)
```



###Naive daily activity: Hourly

```{r, echo=FALSE, warning=FALSE}

with(act_hour[act_hour$Treatment=="Control",], 
     plot(activity_counts ~ jitter(hour_shift, factor=1.3), pch=20, cex=0.2,
          xlab ="hours after initiation", ylab = "hourly activity",
          main = "Activity: Lab Flies ",
          ylim=c(0,400)))

with(act_hour[act_hour$Treatment=="Control",], lines(smooth.spline(y=activity_counts, x = hour_shift),lwd=2))

with(act_hour[act_hour$Treatment=="Spider",], points(activity_counts ~ jitter(hour_shift, factor=1.3), pch=20, cex=0.2, col="red"))
with(act_hour[act_hour$Treatment=="Spider",], lines(smooth.spline(y=activity_counts, x = hour_shift), col="red", lwd=2))

legend(x=15, y=400, legend=c("Control", "Spider"), pch=20, col=c(1, "red"))
rect(xleft=0, xright=10, ybottom = 0, ytop = 830, col="#ffff0032", border=NA)
rect(xleft=22, xright=24, ybottom = 0, ytop = 830, col="#ffff0032", border=NA)

```


###Quick Models

Hourly activity:
```{r}
hour.mod <- lm(activity_counts ~ Treatment + hour_shift + monitor + day,data=act_hour)
summary(hour.mod)
pacf(resid(hour.mod))
```


Correlation Model
```{r}
act_cor_light_mod <- gls(activity_counts ~ Treatment + light + light:Treatment +  hour_shift + monitor + day, correlation = corAR1(form =~1|hour_shift), control = list(singular.ok = TRUE), data=act_hour)
summary(act_cor_light_mod)
confint(act_cor_light_mod)
acf(resid(act_cor_light_mod))
```


###Courtship and Copulation Plots for evolved populations:

Population Mean plots:

```{r, echo=FALSE, warning=FALSE}

copplot <- p1+geom_boxplot()
Courtlat<-p2+geom_boxplot()
coplat <- p3+geom_boxplot()
copdur<-p4+geom_boxplot()
multiplot(copplot, Courtlat, coplat, copdur, cols=2)
```

Population plots together:

```{r, echo=FALSE, warning=FALSE}
Rel_court <- p6+geom_boxplot()
Rel_coplat <- p7+geom_boxplot()
Rel_copdur <- p8+geom_boxplot()
multiplot(Rel_court, Rel_coplat, Rel_copdur, cols=2)
```






